Computing likelihoods under the SMC for a general class of ARGs.

### 2024-04-26 paper.tex
update smc section

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{figures/single_event.png}
    \caption{
        Graphical representation of the events associated with the edge $(p,c,x,y)$.
        The lineage carried by $c$ spans $[x',y)$ until a recombination event (blue dotted line) splits it
        into two segments. The right hand segment coalesces at time $t_p$. The time to
        recombination is thus bounded by $(c. \min(t_p, t_{p'})$.
        \label{fig:likelihood}
    }
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{figures/single_event.png}
    \caption{
        Graphical representation of the events associated with the edge $(p,c,x,y)$.
        The lineage carried by $c$ spans $[x_c,y)$ until a recombination event (blue dotted line) splits it
        into two segments. Left and right hand segments coalesce at times $t_p'$ and $t_p$ respectively,
        bounding the time to recombination by $(c. \min(t_p, t_{p'})$.
        Note that the contribution to the recombination hazard by edge $(p,c,x,y)$ only covers ``half'' of the
        green shaded area. The other half is contributed by edge $(p', c, x_c, x)$. 
        \label{fig:likelihood}
    }
\end{figure}
